Storing messages with multipartite neural cliques

### 2014-07-07 Articles/article.tex
Ajout lettres grecques
....

	edge : $(i, j)$

	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$. Since messages are independent, the density $d$ can be expressed like this :

@@

	Thanks to the memory effect $\gamma$, activated neurons in a non-erased cluster stay activated and are the only ones doing so in their cluster. For neurons in erased clusters, the maximum attainable score is $a(c - c_e)$. Neurons corresponding to the original message achieve this score. Besides the probability for a neuron $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^	{a(c-c_e)}$.

@@

@@

	Correct neurons in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$.

	$P(n_{gc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$

@@

	\begin{align}
	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
	\end{align}

@@

	$P(n_{gc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$

@@

	\newpage
	$\,$
	\newpage	
	\begin{align*}
	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
	\end{align*}

@@

		\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/5portant_erasures_c8l256}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5}
	\end{figure}

@@

	\newpage
	$\,$
	\newpage
	\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/4portant_psi_c8l256e4}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks}
	\end{figure}

	\nocite{*}
	\bibliographystyle{numeric} % Le style est mis entre crochets.
         \bibliography{bibli.bib}
\end{document}

>>>>

	%edge : $(i, j)$

	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$. Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed like this :

@@

	Thanks to the memory effect $\gamma$, activated neurons in a non-erased cluster stay activated and are the only ones doing so in their cluster. For neurons in erased clusters, the maximum attainable score is $a(c - c_e)$. Neurons corresponding to the original message achieve this score. Besides the probability for a neuron $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^{a(c-c_e)}$.

@@

		\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/5portant_erasures_c8l256}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5}
	\end{figure}

@@

	Knowing the density of the network, we can compute the laws for scores achieved by different neurons in different clusters. Subscript $g$ will indicate a neuron being part of the message (it should be activated), subscript $b$ the contrary (the neuron should not be activated). Subscript $a$ means the neuron is activated. Subscript $c$ corresponds to a correct cluster, $e$ to an erroneous cluster.
	Correct neurons in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
	Being connected to a given activated neuron occurs with probability $d$. However corrects neurons see their scores shift, as well as activated neurons respectively thanks to being part of the original message and the memory effect $\gamma$. We can express those probability laws as :

	$P(n_{agc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$

@@

	A message is retrieved after one iteration, if and only if correct neurons achieve strictly the best scores.

	\begin{align}
	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{agc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
	\end{align}

@@

	$P(n_{agc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$

@@

	\newpage

	\begin{align*}
	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = n)^k P(n_{agc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
	\end{align*}

@@

@@

	\newpage
	$\,$
	\newpage
	\begin{figure}
		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks}
	\end{figure}

	Absolute values of slopes diminish for increasing number of activities (resilience is better)

	\nocite{*}
	\bibliographystyle{plain} % Le style est mis entre crochets.
         \bibliography{bibli}
\end{document}
